Testing Quasar Unification: I. Radiative Transfer in Clumpy Winds

### 2015-12-15 paper_mnras.tex
about to shorten angular distribution discussion

We then evaluated these models based on the following criteria:
\begin{itemize}
\item Does the model avoid over-ionization and thus produce UV absorption lines 
with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)?
\item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ \citep[e.g. ][]{shen2011}?
\item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la 
\citep[e.g. ][]{dipompeo2012}?
\item Do the spectra produce \mg\ and \al\ (LoBAL) absorption 
features with $BI > 0$at a small subset of BAL angles?
\item Does the model spectra resemble quasar composite spectra?
\end{itemize}
Where $BI$ is the `Balnicity Index' (Weymann et al. 1991), given by
\begin{equation}
BI = \int^{25000}_{3000} \left( 1 - \frac{f(v)}{0.9} \right) dv.
\end{equation}
The constant $C=0$ everywhere, unless the normalized flux
has satisfied $f(v)<0.9$ continuously for at least $2000$~km~s$^{−1}$, 
whereby $C$ is set to $1$.
In the next section, we present one of the most promising models and discuss
the various successes and failures with respect to the above criteria.
This allows us to gain insight into fundamental geometrical 
and physical constraints and assess the potential for unification. 
We then discuss the sensitivity to key parameters in section 5.
The full grid, including output synthetic spectra and plots can be found at
\url{jhmatthews.github.io/quasar-wind-grid/}.

@@

\section{Results From An Example Model}

Here we describe the results from an example model,
and discuss these results in the context of the criteria 
presented in section 3.4. The parameters of this model are shown in table~2.
Parameters differing from the benchmark model of H13 are 
highlighted with an asterisk. In this section, we examine the physical 
conditions of the flow, and present the synthetic spectra, before comparing
the X-ray properties of this particular model to samples of
quasars and luminous AGN. 
% We also examine trends with inclination in the synthetic spectra, 
% both in terms of the range of ionization states of the absorption lines and equivalent widths of the emission lines.

\begin{table}
\begin{tabular}{p{3cm}p{4cm}}
\hline Next-generation Model Parameters 	&	 Value \\ 
\hline \hline 
$M_{BH}$ 	 &	 $1\times 10^9~\rm{M_{\odot}}$ \\ 
$\dot{M}_{acc}$ 	 &	 $5~M_{\odot}yr^{-1} \simeq 0.2~\dot{M}_{Edd}$\\ 
$\alpha_X$ 	 &	 $-0.9$ \\ 
$L_{X} $ 	 &	 $10^{45}~\rm{erg~s^{-1}}$$^*$ \\ 
$r_{disc}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
$r_{disc}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
$\dot{M}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
$r_{min}$ 	&	 $300r_{g} = 4.4\times10^{16}~{\rm cm}$\\ 
$r_{max}$ 	&	 $600r_{g} = 8.8\times10^{16}~{\rm cm}$ \\ 
$\theta_{min}$ 	&	 $70.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $82.0^{\circ}$ \\ 
$\lambda$ 	&	 $0$ \\ 
$v_{\infty}(r_0)$ 	&	 $v_{esc}(r_0)$ \\ 
$R_v$  	        &	 $10^{19}$cm$^*$ \\ 
$\alpha$ 	&	 $0.6^*$ \\
$f_V$ 	&	 $0.01^*$  \\
$n_x$ 	&	 $100$  \\
$n_z$ 	&	 $200$  \\
\hline 
% Derived Parameters 	&	 Value \\ 
% \hline \hline
% $L_{\nu}(2500\mbox{\scriptsize{\AA}})$&	 $6.3\times10^{30}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{\nu}(2keV)$   &	 $1.2\times10^{25}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{bol}$ 	 &	 $2.4\times10^{46}~\rm{ergs~s^{-1}}$\\
% $M_{bol}$ 	 &	 -27.4\\ 
% $M_u$            &	 -26.2\\ 
% $\alpha_{OX} $ 	 &	 -2.2\\ 
\end{tabular}
\caption{Wind geometry parameters 
used in the model, as defined in the text and figure 1.
Parameters differing from the benchmark model of H13 are 
highlighted with an asterisk.}
\label{wind_param}
\end{table}

@@

The main motivation for including a treatment of clumping was
to avoid over-ionization of the wind in the presence of strong X-rays. 
Having verified that strong BALs appear in the synthetic spectra,
it is also important to assess whether the X-ray properties of this
example model agree well with quasar and BALQSO samples for the relevant
inclinations.

@@

 We have demonstrated that our example model successfully reproduces much of
 the phenomenology of luminous AGN and quasars, with a few exceptions.
 Here, we discuss these shortcomings, by discussing parameter sensitivity
 and the dependence of line EWs on inclination.

>>>>

We then evaluated these models based on whether their synthetic spectra exhibited the 
following properties of quasars and BALQSOs:

\begin{itemize}
\item UV absorption lines 
with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)
\item Line emission emerging at low inclinations, with $EW\sim40\AA$ in \civ\ \citep[e.g. ][]{shen2011}
\item H recombination lines with $EW\sim50\AA$ in \la\ \citep[e.g. ][]{shen2011}
\item  \mg\ and \al\ (LoBAL) absorption features with $BI > 0$ at a small subset of BAL angles
\item Verisimilitude with quasar composite spectra.
\end{itemize}
Where $BI$ is the `Balnicity Index' (Weymann et al. 1991), given by
\begin{equation}
BI = \int^{25000}_{3000} \left( 1 - \frac{f(v)}{0.9} \right) dv.
\end{equation}
The constant $C=0$ everywhere, unless the normalized flux
has satisfied $f(v)<0.9$ continuously for at least $2000$~km~s$^{−1}$, 
whereby $C$ is set to $1$.

% the following criteria:
% \begin{itemize}
% \item Do the synthetic spectra exhibit UV absorption lines 
% with $BI > 0$ at $\sim20\%$ of viewing angles (e.g. Knigge et al. 2010)?
% \item Do the synthetic spectra show  line emission emerge at low inclinations, with $EW\sim40\AA$ in \civ \citep[e.g. ][]{shen2011}?
% \item Do H recombination lines appear in the spectra, $EW\sim50\AA$ in \la 
% \citep[e.g. ][]{shen2011}?
% \item Do the spectra produce \mg\ and \al\ (LoBAL) absorption 
% features with $BI > 0$ at a small subset of BAL angles?
% \item Does the model spectra resemble quasar composite spectra?
% \end{itemize}
% Where $BI$ is the `Balnicity Index' (Weymann et al. 1991), given by
% \begin{equation}
% BI = \int^{25000}_{3000} \left( 1 - \frac{f(v)}{0.9} \right) dv.
% \end{equation}
% The constant $C=0$ everywhere, unless the normalized flux
% has satisfied $f(v)<0.9$ continuously for at least $2000$~km~s$^{−1}$, 
% whereby $C$ is set to $1$.

In the next section, we present one of the most promising models,
which we refer to as the fiducial model, and discuss
the various successes and failures with respect to the above criteria.
This allows us to gain insight into fundamental geometrical 
and physical constraints and assess the potential for unification. 
We then discuss the sensitivity to key parameters in section 5.
The full grid, including output synthetic spectra and plots can be found at
\url{jhmatthews.github.io/quasar-wind-grid/}.

@@

\section{Results From A Fiducial Model}
Here we describe the results from a fiducial model,
and discuss these results in the context of the criteria 
presented in section 3.4. The parameters of this model are shown in table~2.
Parameters differing from the benchmark model of H13 are 
highlighted with an asterisk. In this section, we examine the physical 
conditions of the flow, and present the synthetic spectra, before comparing
the X-ray properties of this particular model to samples of
quasars and luminous AGN. 
% We also examine trends with inclination in the synthetic spectra, 
% both in terms of the range of ionization states of the absorption lines and equivalent widths of the emission lines.

\begin{table}
\begin{tabular}{p{3cm}p{4cm}}
\hline Fiducial Model Parameters 	&	 Value \\ 
\hline \hline 
$M_{BH}$ 	 &	 $1\times 10^9~\rm{M_{\odot}}$ \\ 
$\dot{M}_{acc}$ 	 &	 $5~M_{\odot}yr^{-1} \simeq 0.2~\dot{M}_{Edd}$\\ 
$\alpha_X$ 	 &	 $-0.9$ \\ 
$L_{X} $ 	 &	 $10^{45}~\rm{erg~s^{-1}}$$^*$ \\ 
$r_{disc}(min)=r_{X}$   &	 $6r_g=8.8\times10^{14}~{\rm cm}$ \\ 
$r_{disc}(max)$   &	 $3400r_g = 5\times10^{17}~{\rm cm}$ \\ 
$\dot{M}_{wind}$  &	 $5~M_{\odot}yr^{-1}$ \\ 
$r_{min}$ 	&	 $300r_{g} = 4.4\times10^{16}~{\rm cm}$\\ 
$r_{max}$ 	&	 $600r_{g} = 8.8\times10^{16}~{\rm cm}$ \\ 
$\theta_{min}$ 	&	 $70.0^{\circ}$ \\ 
$\theta_{max}$ 	&	 $82.0^{\circ}$ \\ 
$\lambda$ 	&	 $0$ \\ 
$v_{\infty}(r_0)$ 	&	 $v_{esc}(r_0)$ \\ 
$R_v$  	        &	 $10^{19}$cm$^*$ \\ 
$\alpha$ 	&	 $0.6^*$ \\
$f_V$ 	&	 $0.01^*$  \\
$n_x$ 	&	 $100$  \\
$n_z$ 	&	 $200$  \\
\hline 
% Derived Parameters 	&	 Value \\ 
% \hline \hline
% $L_{\nu}(2500\mbox{\scriptsize{\AA}})$&	 $6.3\times10^{30}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{\nu}(2keV)$   &	 $1.2\times10^{25}~\rm{ergs~s^{-1}~Hz^{-1}}$\\ 
% $L_{bol}$ 	 &	 $2.4\times10^{46}~\rm{ergs~s^{-1}}$\\
% $M_{bol}$ 	 &	 -27.4\\ 
% $M_u$            &	 -26.2\\ 
% $\alpha_{OX} $ 	 &	 -2.2\\ 
\end{tabular}
\caption{Wind geometry parameters 
used in the fiducial model, as defined in the text and figure 1.
Parameters differing from the benchmark model of H13 are 
highlighted with an asterisk.}
\label{wind_param}
\end{table}

@@

The main motivation for including a treatment of clumping was
to avoid over-ionization of the wind in the presence of strong X-rays. 
Having verified that strong BALs appear in the synthetic spectra,
it is also important to assess whether the X-ray properties of this
fiducial model agree well with quasar and BALQSO samples for the relevant
inclinations.

@@

 We have demonstrated that our fiducial model successfully reproduces much of
 the phenomenology of luminous AGN and quasars, with a few exceptions.
 Here, we discuss these shortcomings, by discussing parameter sensitivity
 and the dependence of line EWs on inclination.
